---
title: "R Notebook"
output: html_notebook
---


```{r}
# Clear Global Environment
rm(list=ls(all=TRUE))

# please change to your working directory
setwd("/Users/zhaozhun/Dropbox/Zhao Zhun-FYP/code/SVCJ-master")

# -----------------
# Libraries loading
# -----------------

# List of libraries to be used
lib <- list("truncnorm", "MASS", "MCMCpack", "ggplot2", "readr", "Rlab")

# Installing or calling the libraries
invisible(lapply(lib, function(x){
  result <- library(x, logical.return=T, character.only =T)
  if(result == F) install.packages(x)
  library(x, character.only =T)
  print(paste0(x, " loaded"))
}))
rm(lib)
```

```{r}
# ------------------------------------------------------
# Load SVCJ parameters (comming from svcj_all_cryptos.R)
# ------------------------------------------------------

load("ETH_svcj.Rda")
load("BTC_svcj.Rda")
load("LTC_svcj.Rda")


btcP.df <- read.csv(file = 'BTC-USD.csv',stringsAsFactors = FALSE)
ethP.df <- read.csv(file = 'ETH-USD.csv',stringsAsFactors = FALSE)
ltcP.df <- read.csv(file = 'LTC-USD.csv',stringsAsFactors = FALSE)
# --------------------------------------
# Price Simulation using SVCJ parameters
# --------------------------------------
```
```{r}
# Some initial set up parameters: 
n      = 21  # Number of observaions in each simulation (i.e number of future days) => row 1 is t0 => 2 = t+1
iter = 5000 # Number of price paths
```
```{r}
#load data

BTC_initial_train.df <-btcP.df[1:1462,]
ETH_initial_train.df <-ethP.df[1:1462,]
LTC_initial_train.df <-ltcP.df[1:1462,]
```

```{r}
# svcj version - not spplitting training-test internally 
svcj_model <- function(P, N = 5000, n = 1000) {

# Generate returns Y from initial prices P

#training.df <- P[1:1462,]
logP <- log(P$Adj.Close)
Y <- diff(logP)*sqrt(250)
#Y <- diff(logP)
  
one <- rep(1, length = length(Y))

# Prior distribution of hyperparameter values
a=0
A=25 # prior for mu
b = matrix(c(0,0), nrow = 2, ncol = 1) # prior for alpha and beta
B = diag(2) # prior for alpha and beta
c = 2.5 # prior for sigma2_v
C = 0.1 # prior for sigma2_v
d = 10 # prior for mu_v
D = 20 # prior for mu_v
e = 0 
E = 100 # prior for mu_y
f = 10 # prior for sigma2_y
F = 40 # prior for sigma2_y
g = 0
G = 4
k = 2 # prior for lambda
K = 40 # prior for lambda
tmp = vector()

# Starting values
# m=mu
m=a 
msum=0 
m2sum=0

# kappa=-alpha/beta, the theta in equation 1
kappa = 0 
kappasum = 0 
kappa2sum = 0     

# alpha in equation 3
alpha = b[1]
alphasum = 0 
alpha2sum = 0

# beta in eq.3
beta = b[2] 
betasum = 0 
beta2sum = 0

# sigma_v in eq.3
s2V = C/(c - 2)
s2Vsum = 0
s2V2sum = 0

# the relation between w1 ad w2
rho = 0 
rhosum = 0 
rho2sum = 0

# mu_v, the param in expoential distr. of Z_v
# (jump size in variance)
mV = D/(d-2) 
mVsum = 0
mV2sum = 0         

# mu_y, the mean of jump size in price Z_y
mJ = e 
mJsum = 0 
mJ2sum = 0

# sigma_Y, the variance of jump size in price Z_y 
s2J = F/(f - 2) 
s2Jsum = 0 
s2J2sum = 0

# rho param in the jump size of price
rhoJ = g 
rhoJsum = 0 
rhoJ2sum = 0

# jump intensity
lambda = 0
lambdasum = 0
lambda2sum = 0

# Initial values for variance_t
V = 0.1*(Y - mean(Y))^2 + 0.9*var(Y)
Vsum = 0
Vsum2 = 0

# J = data(2:end,3);
J = abs(Y) - mean(Y) > 2 * sd(Y); 
Jsum = 0

# the jump size in volatility, Z_t^y
XV = rexp(length(Y), rate = 1/mV)
XVsum = 0

# the jump size in price
X = rnorm(n = length(Y), mean = (mJ+XV*rhoJ), sd = s2J^0.5)
Xsum = 0
stdevrho = 0.01
dfrho = 6.5
stdevV = 0.9
dfV = 4.5
acceptsumV = rep(0,length(V))
acceptsumrho = 0
acceptsums2V = 0
Z = rep(1, length(Y))

# matrix for params
test = matrix(0, nrow = N, ncol = 10)

for (i in 1:N){
  
  print(paste0("Iteration ", i, " of ", N))
  Rho = 1/(1-rho^2)
  V0 = V[1]
  
  # Draw m(i+1)
  Q=(Y - X*J - rho/s2V^0.5*(V-append(V0, V[1:length(V)-1])*(1+beta)-alpha-J*XV))/(append(V0, V[1:length(V)-1]))^0.5
  W = (1/append(V0, V[1:length(V)-1]))^0.5
  
  As = solve(solve(A) + 1/(1-rho^2)*(t(W)%*%W))
  as = As*(solve(A)*a+1/(1-rho^2)*(t(W)%*%Q))
  
  m = rnorm(n = 1,mean = as, sd = As^0.5)
  
  if (i>n){
    msum = msum + m
    m2sum = m2sum + m^2
  }
  
  # (alpha, beta)
  # Expected return
  eY = Y - Z*m - X*J
  # Expected variance
  eV = V - append(V0, V[1:length(V)-1]) - XV*J
  Q = (eV - rho*sqrt(s2V)*eY)/append(V0, V[1:length(V)-1])^0.5
  W = cbind(1/append(V0, V[1:length(V)-1])^0.5, append(V0, V[1:length(V)-1])^0.5)
  Bs = solve(solve(B) + as.vector(Rho/s2V)*t(W)%*%W)
  bs = Bs%*%(solve(B)%*%b + as.vector(Rho/s2V)*(t(W)%*%Q))
  library(MASS)
  temp = MASS::mvrnorm(n=1, mu = bs, Sigma = Bs)  
  alpha = temp[1]
  beta = temp[2]
  kappa = -alpha/beta
  
  if (i>n){
    alphasum = alphasum + alpha
    alpha2sum = alpha2sum + alpha^2
    betasum = betasum + beta
    beta2sum = beta2sum + beta^2
    kappasum = kappasum + kappa
    kappa2sum = kappa2sum + kappa^2
  }
  
  # s2V
  cs = c + length(Y)
  Cs = C + sum(((V-append(V0, V[1:length(V)-1])-alpha-beta*append(V0, V[1:length(V)-1])-XV*J)^2)/append(V0, V[1:length(V)-1]))
  #install.packages("MCMCpack")
  library(MCMCpack)
  s2Vprop = MCMCpack::riwish(cs, Cs)
  # iwishrnd(Tau,df) general formula in Matlab
  q = exp(-0.5*sum((V-append(V0, V[1:length(V)-1])*(1+beta) - alpha - J*XV)^2/(as.vector(s2Vprop)*append(V0, V[1:length(V)-1])) -
                     (V - append(V0, V[1:length(V)-1])*(1+beta) - alpha - J*XV)^2/(s2V*append(V0, V[1:length(V)-1]))))
  p = exp(-0.5*sum((V-append(V0, V[1:length(V)-1])*(1+beta) - alpha - J*XV - rho*as.vector(s2Vprop)^0.5*(Y-Z*m-J*X))^2/
                     ((1-rho^2)*as.vector(s2Vprop)*append(V0, V[1:length(V)-1])) -
                     (V-append(V0, V[1:length(V)-1])*(1+beta) - alpha - J*XV - rho*s2V^0.5*(Y-Z*m-J*X))^2/
                     ((1-rho^2)*s2V*append(V0, V[1:length(V)-1]))))
  x = ifelse(is.nan(min(p/q,1)),1,min(p/q,1))
  u = runif(1)
  
  if (x>u){
    s2V = s2Vprop
    if (i>n){
      acceptsums2V = acceptsums2V + 1
    }
  }    
  
  if (i>n){
    s2Vsum = s2Vsum + s2V
    s2V2sum = s2V2sum + s2V^2
  } 
  
  # rho
  # Draw a candidate for rho(i+1)
  # draw rhoc from a t distribution with 8 df and std of 0.2666
  rhoprop = rho + stdevrho*rt(n = length(rho), df = dfrho)
  if (abs(rhoprop)<1){
    p = (sqrt( 1 - rho^2 )/ sqrt( 1 - rhoprop^2 ))^T * exp( sum( - 1 / ( 2 * ( 1 - rhoprop^2 ) ) *
                                                                   ( Y - Z*m - J*X - as.vector(rhoprop / s2V^0.5) * ( V - alpha - append(V0, V[1:length(V)-1]) * ( 1 + beta ) - J*XV ) )^2/
                                                                   append(V0, V[1:length(V)-1]) + 1 / ( 2 * ( 1 - rho^2 ) ) *
                                                                   ( Y - Z*m - J*X - as.vector(rho / s2V^0.5) * ( V[1:length(V)] - alpha - append(V0, V[1:length(V)-1]) * ( 1 + beta ) - J*XV ) )^2/
                                                                   append(V0, V[1:length(V)-1]) ) )
    
    u = runif(1)
    x = min(p,1)
    if (x>u){
      rho = rhoprop
      if (i>n){
        acceptsumrho = acceptsumrho + 1
      } 
    } 
  }
  
  if (i>n){
    rhosum = rhosum + rho
    rho2sum = rho2sum + rho^2
  }
  
  # mV
  ds= d + 2*length(Y)
  Ds = D + 2*sum(XV)
  library(MCMCpack)
  mV = MCMCpack::riwish(ds, Ds)
  
  if (i>n){
    mVsum = mVsum + mV
    mV2sum = mV2sum + mV^2
  }
  
  # mJ
  Es = 1/(length(Y)/s2J + 1/E)
  es = Es * (sum((X-XV*rhoJ)/s2J)+ e/E)
  mJ = rnorm(n=1, mean= es, sd = Es^0.5)
  if (i>n){
    mJsum = mJsum + mJ
    mJ2sum = mJ2sum + mJ^2
  } 
  
  # s2Y
  fs = f + length(Y)
  Fs = F + sum((X-mJ-rhoJ*XV)^2)
  s2J = MCMCpack::riwish(fs,Fs)
  if (i>n){
    s2Jsum = s2Jsum + s2J
    s2J2sum = s2J2sum + s2J^2
  }
  
  # rhoJ
  Gs = solve(sum(XV^2)/s2J + 1/G)
  gs = Gs * (sum((X - mJ)*XV)/s2J + g/G);
  rhoJ = rnorm(n=1,mean = gs,sd=Gs^0.5); 
  if (i > n)  {
    rhoJsum = rhoJsum + rhoJ 
    rhoJ2sum = rhoJ2sum + rhoJ^2
  }
  
  
  # lambda
  ks = k + sum(J)
  Ks = K + length(Y) - sum(J)
  lambda = rbeta(n = 1,ks, Ks)
  
  if (i>n){
    lambdasum = lambdasum + lambda
    lambda2sum = lambda2sum + lambda^2
  }
  
  # J
  eY1 = Y - Z*m - X
  eY2 = Y - Z*m
  eV1 = V - append(V0, V[1:length(V)-1]) - alpha - beta*append(V0, V[1:length(V)-1]) - XV
  eV2 = V - append(V0, V[1:length(V)-1]) - alpha - beta*append(V0, V[1:length(V)-1])
  p1 = lambda*exp( -0.5 * ( ((eY1 - (rho/sqrt(s2V))*eV1)^2)/((1-rho^2)*append(V0, V[1:length(V)-1])) + (eV1^2)/(s2V*append(V0, V[1:length(V)-1])) ) )
  p2 = (1 - lambda) * exp( -0.5 * ( ((eY2 - (rho/sqrt(s2V))*eV2)^2)/((1-rho^2)*append(V0, V[1:length(V)-1])) + (eV2^2)/(s2V*append(V0, V[1:length(V)-1])) ) )
  p = p1/(p1 + p2)
  tmp= cbind(tmp, p1, p2, p)
  
  u = runif(n = length(Y))
  J = as.double(u < p)
  
  if (i>n){
    Jsum = Jsum + J
  }
  
  Jindex = which(J == 1)
  
  # XV
  XV[as.logical(!J)] = rexp(n = (length(Y) - sum(J)), rate = 1/mV)
  if (length(Jindex) != 0){
    if (Jindex[1] == 1) {
      t = 1
      eV = V[1] - V0 - alpha - beta*V0;
      eY = Y[1] - Z[1]*m - X[1]
      H = solve( 1 /((1 - rho^2)*s2V*V0) + rhoJ^2/s2J )
      h = H * ((eV-rho*sqrt(s2V)*eY)/((1 - rho^2)*s2V*V0) + rhoJ*(X[1] - mJ)/s2J - 1/mV)
      if (h+5*sqrt(H) > 0) { 
        XV[1] = truncnorm::rtruncnorm(n = 1, mean = h, sd = sqrt(H), a=0, b=h+5*sqrt(H))
      } else {
        XV[1] = 0
      }
      if (is.infinite(XV[1]) | is.nan(XV[1])) { 
        XV[1] = 0 
      }
    } else {  
      t = Jindex[1]
      eV = V[t] - V[t-1] - alpha - beta*V[t-1]
      eY = Y[t] - Z[t]*m - X[t]
      H = solve( 1 /((1 - rho^2)*s2V*V[t-1]) + rhoJ^2/s2J )
      h = H * ((eV-rho*sqrt(s2V)*eY)/((1 - rho^2)*s2V*V[t-1]) + rhoJ*(X[t] - mJ)/s2J - 1/mV)
      if (h+5*sqrt(H) > 0) {
        XV[t] = truncnorm::rtruncnorm(n = 1, mean = h, sd = sqrt(H), a=0, b=h+5*sqrt(H))
      } else { 
        XV[t] = 0
      }
      if (is.infinite(XV[t]) |is.nan(XV[t])) {
        XV[t] = 0
      }
    }
    if (length(Jindex) > 1) {
      for (t in Jindex[2:length(Jindex)]) {
        eV = V[t] - V[t-1] - alpha - beta*V[t-1]
        eY = Y[t] - Z[t]*m - X[t]
        H = solve( 1 /((1 - rho^2)*s2V*V[t-1]) + rhoJ^2/s2J )
        h = H * ((eV-rho*sqrt(s2V)*eY)/((1 - rho^2)*s2V*V[t-1]) + rhoJ*(X[t] - mJ)/s2J - 1/mV)
        if (h+5*sqrt(H) > 0) { 
          XV[t] = truncnorm::rtruncnorm(n = 1, mean = h, sd = sqrt(H), a=0, b=h+5*sqrt(H))
        } else { 
          XV[t] = 0
        }
        if (is.infinite(XV[t]) | is.nan(XV[t])) {
          XV[t] = 0
        }
      }
    }
  }
  
  if (i > n) {
    XVsum = XVsum + XV
  }
  
  
  # X
  X[as.logical(!J)] = rnorm(mJ + rhoJ*XV[as.logical(!J)], sd = sqrt(s2J))
  if (length(Jindex) != 0){
    if (Jindex[1] == 1) {
      t = 1
      eV = V[1] - V0 - alpha - beta*V0 - XV[1]
      eY = Y[1] - Z[1]*m
      L = solve(1/((1 - rho^2)*V0) + 1/s2J)
      l = L * ( (eY - (rho/sqrt(s2V))*eV)/((1 - rho^2)*V0) + (mJ + rhoJ*XV[1])/s2J )
      X[1] = rnorm(n=1,l,sqrt(L))
    } else {
      t = Jindex[1]
      eV = V[t] - V[t-1] - alpha - beta*V[t-1] - XV[t]
      eY = Y[t] - Z[t]*m
      L = solve(1/((1 - rho^2)*V[t-1]) + 1/s2J)
      l = L * ( (eY - (rho/sqrt(s2V))*eV)/((1 - rho^2)*V[t-1]) + (mJ + rhoJ*XV[t])/s2J )
      X[t] = rnorm(n=1,l,sqrt(L))
    }
    if (length(Jindex) > 1) {
      for (t in Jindex[2:length(Jindex)]) {
        eV = V[t] - V[t-1] - alpha - beta*V[t-1] - XV[t]
        eY = Y[t] - Z[t]*m
        L = solve(1/((1 - rho^2)*V[t-1]) + 1/s2J)
        l = L * ( (eY - (rho/sqrt(s2V))*eV)/((1 - rho^2)*V[t-1]) + (mJ + rhoJ*XV[t])/s2J )
        X[t] = rnorm(n=1,l,sqrt(L))
      }
    }
  }
  if (i > n) {
    Xsum = Xsum + X
  }
  
  
  # Draw V
  epsilon = rt(n=length(Y), dfV) 
  mv = 0 # mean of t distribution with parameter dfV
  v = dfV/(dfV-2) # # variance of t distribution with parameter dfV
  epsilon = (stdevV/sqrt(v)) * epsilon
  if (i == floor(n / 2)){
    Vindex1 = which(Vsum2 > quantile(Vsum2, 0.925))
    Vindex2 = which(Vsum2 > quantile(Vsum2, 0.75) & Vsum2 < quantile(Vsum2, 0.925))
    Vindex3 = which(Vsum2 < quantile(Vsum2, 0.25) & Vsum2 > quantile(Vsum2, 0.025))
    Vindex4 = which(Vsum2 < quantile(Vsum2, 0.025))
  }
  if (i > floor(n / 2) - 1) {
    epsilon[Vindex1] = 1.35 * epsilon[Vindex1]
    epsilon[Vindex2] = 1.25 * epsilon[Vindex2]
    epsilon[Vindex3] = 0.75 * epsilon[Vindex3]
    epsilon[Vindex4] = 0.65 * epsilon[Vindex4]
  }
  j = 1
  Vprop = V + epsilon
  p1 = max(0,exp( -0.5 * ( ( Y[j+1] - Z[j+1]*m[1]  - J[j+1]*X[j+1] - rho / s2V^0.5 *(V[j+1] - Vprop[j] - alpha - Vprop[j] * beta - J[j+1]*XV[j+1] ) )^2/( (1 - rho^2) * Vprop[j] ) +
                             ( Y[j] - Z[j]*m[1]  - J[j]*X[j] - rho / s2V^0.5 *(Vprop[j] - V0 - alpha - V0 * beta - J[j]*XV[j]))^2/( (1 - rho^2) * V0 ) +
                             ( V[j+1] - Vprop[j] - alpha - Vprop[j] * beta - J[j+1]*XV[j+1] )^2/( s2V * Vprop[j] ) +
                             ( Vprop[j] - V0 - alpha - V0 * beta - J[j]*XV[j])^2/( s2V * V0 ) ) ) / Vprop[j])
  p2 = max(0,exp( -0.5 * ( ( Y[j+1] - Z[j+1]*m[1]  - J[j+1]*X[j+1] - rho / s2V^0.5 *(V[j+1] - V[j] - alpha - V[j] * beta - J[j+1]*XV[j+1] ) )^2/( (1 - rho^2) * V[j] ) +
                             ( Y[j] - Z[j]*m[1]  - J[j]*X[j] -rho / s2V^0.5 *(V[j] - V0 - alpha - V0 * beta - J[j]*XV[j]) )^2/( (1 - rho^2) * V0 ) +
                             ( V[j+1] - V[j] - alpha - V[j] * beta - J[j+1]*XV[j+1])^2/( s2V * V[j] ) +
                             ( V[j] - V0 - alpha - V0 * beta - J[j]*XV[j])^2/( s2V * V0 ) ) ) / V[j])
  if (p2 != 0) {
    acceptV = min(p1/p2, 1)
  } else if( p1 > 0){ 
    acceptV = 1 
  } else { 
    acceptV = 0
  }
  
  u = runif(length(Y))
  if (u[j] < acceptV) {
    V[j] = Vprop[j]
    if (i > n) {
      acceptsumV[j] = acceptsumV[j] + 1
    }
  }
  
  for (j in 2:length(Y)-1) {
    p1 = max(0,exp( -0.5 * ( ( Y[j+1] - Z[j+1]*m[1]  - J[j+1]*X[j+1] - rho / s2V^0.5 *(V[j+1] - Vprop[j] - alpha - Vprop[j] * beta - J[j+1]*XV[j+1]) )^2/( (1 - rho^2) * Vprop[j] ) +
                               ( Y[j] - Z[j]*m[1]  - J[j]*X[j] - rho / s2V^0.5 *(Vprop[j] - V[j-1] - alpha - V[j-1] * beta - J[j]*XV[j] ) )^2/( (1 - rho^2) * V[j-1] ) +
                               ( V[j+1] - Vprop[j] - alpha - Vprop[j] * beta - J[j+1]*XV[j+1])^2/( s2V * Vprop[j] ) +
                               ( Vprop[j] - V[j-1] - alpha - V[j-1] * beta - J[j]*XV[j])^2/( s2V * V[j-1] ) ) ) / Vprop[j])
    p2 = max(0,exp( -0.5 * ( ( Y[j+1] - Z[j+1]*m[1]  - J[j+1]*X[j+1] - rho / s2V^0.5 *(V[j+1] - V[j] - alpha - V[j] * beta - J[j+1]*XV[j+1]) )^2/( (1 - rho^2) * V[j] ) +
                               ( Y[j] - Z[j]*m[1] - J[j]*X[j] - rho / s2V^0.5 *(V[j] - V[j-1] - alpha - J[j]*XV[j] - V[j-1] * beta ) )^2/( (1 - rho^2) * V[j-1] ) +
                               ( V[j+1] - V[j] - alpha - V[j] * beta - J[j+1]*XV[j+1])^2/( s2V * V[j] ) +
                               ( V[j] - V[j-1] - alpha - V[j-1] * beta - J[j]*XV[j])^2/( s2V * V[j-1] ) ) ) / V[j])
    if (p2 != 0){
      acceptV = min(p1/p2, 1)
    } else if (p1 > 0){
      acceptV = 1 
    } else {
      acceptV = 0
    }
    
    if (u[j] < acceptV) { 
      V[j] = Vprop[j]
      if (i > n) {
        acceptsumV[j] = acceptsumV[j] + 1
      }
    }
  }
  
  j = length(Y)
  p1 = max(0,exp( -0.5 * ( ( Y[j] - Z[j]*m[1]  - J[j]*X[j] - rho / s2V^0.5 *(Vprop[j] - V[j-1] - alpha - V[j-1] * beta - J[j]*XV[j]) )^2/( (1 - rho^2) * V[j-1] ) +
                             ( Vprop[j] - V[j-1] - alpha - V[j-1] * beta - J[j]*XV[j])^2/( s2V * V[j-1] ) ) ) / Vprop[j]^0.5)
  p2 = max(0,exp( -0.5 * ( ( Y[j] - Z[j]*m[1]  - J[j]*X[j] - rho / s2V^0.5 *(V[j] - V[j-1] - alpha - V[j-1] * beta - J[j]*XV[j]) )^2/( (1 - rho^2) * V[j-1] ) +
                             ( V[j] - V[j-1] - alpha - V[j-1] * beta  - J[j]*XV[j])^2/( s2V * V[j-1] ) ) ) / V[j]^0.5)
  
  if (ifelse(is.nan(p2),TRUE,p2 != 0)) {
    acceptV = ifelse(is.nan(min(p1/p2, 1)),0,min(p1/p2, 1))
  } else if (p1 > 0){
    acceptV = 1
  } else {
    acceptV = 0
  }
  
  if (u[j] < acceptV) {
    V[j] = Vprop[j]
    if (i > n) {
      acceptsumV[j] = acceptsumV[j] + 1
    }
  }
  
  if (i > n) {
    Vsum = Vsum + V
  }
  if (i > floor(n / 2) - 100 | i < floor(n / 2)) { 
    Vsum2 = Vsum2 + V
  }
  
  test[i,] = c(m, mJ, s2J, lambda, alpha, beta,  rho, s2V, rhoJ, mV)
  
}

parameters <- data.frame(parameter = as.character(c("mu", "mu_y", "sigma_y", "lambda", "alpha", "beta", "rho", "sigma_v", "rho_j", "mu_v")), 
                               mean = round(c(msum/(N-n), mJsum/(N-n), s2Jsum/(N-n),lambdasum/(N-n),alphasum/(N-n),betasum/(N-n),rhosum/(N-n),s2Vsum/(N-n),rhoJsum/(N-n),mVsum/(N-n)),3),
                               sd = round(c((m2sum/(N-n)-(msum/(N-n))^2)^0.5,
                                      (mJ2sum/(N-n)-(mJsum/(N-n))^2)^0.5,
                                      (s2J2sum/(N-n)-(s2Jsum/(N-n))^2)^0.5,
                                      (lambda2sum/(N-n)-(lambdasum/(N-n))^2)^0.5,
                                      (alpha2sum/(N-n)-(alphasum/(N-n))^2)^0.5,
                                      (beta2sum/(N-n)-(betasum/(N-n))^2)^0.5,
                                      (rho2sum/(N-n)-(rhosum/(N-n))^2)^0.5,
                                      (s2V2sum/(N-n)-(s2Vsum/(N-n))^2)^0.5,
                                      (rhoJ2sum/(N-n)-(rhoJsum/(N-n))^2)^0.5,
                                      (mV2sum/(N-n)-(mVsum/(N-n))^2)^0.5),3)
                         )

test <- as.data.frame(test)
colnames(test) <- c("mu", "mu_y", "sigma_y", "lambda", "alpha", "beta", "rho", "sigma_v", "rho_j", "mu_v")

                               
jump_vol = XVsum/(N-n)*round(Jsum/(N-n))
jump_price = Xsum/(N-n)*round(Jsum/(N-n))
vol = Vsum/(N-n)
sig = vol^0.5
resid = (Y[2:length(Y)] - msum/(N-n) - jump_price[2:length(jump_price)])/sig[1:length(sig)-1]

svcj_results <- setNames(list(parameters, test, jump_vol, jump_price, vol, resid), 
                         c("parameters", "param_evolution" ,"jumps_volatility", "jumps_price", "volatility", "residuals"))
return(svcj_results)
 
print(svcj_results$parameters)

}
```




simulation loop
BTC
```{r warning=FALSE}
simulated_returnsVol_BTC = list()


  parameters = BTC_result$parameters
  mu = parameters[1,2]
  mu_y = parameters[2,2]  
  sigma_y = parameters[3,2]  
  lambda = parameters[4,2]
  alpha = parameters[5,2]
  beta = parameters[6,2]
  rho = parameters[7,2]
  sigma_v = parameters[8,2]
  rho_j = parameters[9,2]
  mu_v = parameters[10,2]
  kappa = -(alpha/beta)
  theta = alpha/kappa
  
  # Create empty vectors to store the simulated values
  V    = matrix(0, nrow = iter, ncol  = n)  # Volatility of log return
  iV   = matrix(0, nrow = iter, ncol  = n)
  Y    = matrix(0, nrow = iter, ncol  = n)  # Log return
  Jv   = matrix(0, nrow = iter, ncol  = n)  # Jumps in volatility
  Jy   = matrix(0, nrow = iter, ncol  = n)  # Jumps in log return
  V[,1] = BTC_result$volatility[length(BTC_result$volatility)]  # Initial value of volatility = previous estimated vol
  iV[,1] = BTC_result$volatility[length(BTC_result$volatility)]
    
  
  for (i in 2:n) {
      if (i>2){
        startIndex = 1+i-2
        endIndex = 1462+i-2
        intermediate_fit <- svcj_model(btcP.df[startIndex:endIndex,])
        iV[,i-1]=intermediate_fit$volatility[length(intermediate_fit$volatility)]
          parameters = intermediate_fit$parameters
            mu = parameters[1,2]
            mu_y = parameters[2,2]  
            sigma_y = parameters[3,2]  
            lambda = parameters[4,2]
            alpha = parameters[5,2]
            beta = parameters[6,2]
            rho = parameters[7,2]
            sigma_v = parameters[8,2]
            rho_j = parameters[9,2]
            mu_v = parameters[10,2]
            kappa = -(alpha/beta)
            theta = alpha/kappa
      }
      Z = mvrnorm(n = iter, mu = c(0,0), Sigma = matrix(c(1,rho,rho,1), nrow = 2))  # Standard normal random value
      Z1 = Z[,1]
      Z2 = Z[,2] 
      J = rbern(n = iter, prob = lambda)  # Bernoulli distributed random value with lambda = 0.051 for determining whether a jump exists
      XV       = rexp(n = iter, rate = 1/mu_v)  # Exponential distributed random value with mV = 0.709 for jump size in volatility
      X        = rnorm(n = iter, mean = mu_y + rho_j * XV, sd = sigma_y)  # Jump size of log return
      #V[i]     = alpha + beta*V[i-1] + sigma_v*sqrt(V[i-1])*Z2 + XV*J  # Volatilty
      V[,i]     = kappa * theta + (1 - kappa) * iV[,i-1] + sigma_v*sqrt(iV[,i-1])*Z2 + XV*J
      Y[,i]     = mu + sqrt(iV[,i-1])*Z1 + X*J  # Log return
      Jv[,i]    = XV*J  # Jumps in volatilty (0 in case of no jump)
      Jy[,i]    = X*J  # Jumps in log return (0 in case of no jump)
      print(paste0("Simulation ",i," of ", n, " for BTC"))
    }

simulated_returnsVol_BTC <- setNames(list(Y, V,iV), 
                                               c("simulated_returns", "simulated_volatility","estimated_volatility"))

save(simulated_returnsVol_BTC, file = "simulated_returns_BTC.Rda")

rm(parameters, alpha, beta, crypto, i, iter, J, 
   Jv, Jy, kappa, lambda, mu, mu_v, mu_y, n, rho, rho_j, sigma_v, sigma_y,
   theta, V, X, XV, Y, Z1, Z2, Z,intermediate_fit,startIndex,endIndex,iV)


```

ETH
```{r warning=FALSE}
n      = 21  # Number of observaions in each simulation (i.e number of future days) => row 1 is t0 => 2 = t+1
iter = 5000 # Number of price paths
simulated_returnsVol_ETH = list()


  parameters = ETH_result$parameters
  mu = parameters[1,2]
  mu_y = parameters[2,2]  
  sigma_y = parameters[3,2]  
  lambda = parameters[4,2]
  alpha = parameters[5,2]
  beta = parameters[6,2]
  rho = parameters[7,2]
  sigma_v = parameters[8,2]
  rho_j = parameters[9,2]
  mu_v = parameters[10,2]
  kappa = -(alpha/beta)
  theta = alpha/kappa
  
  # Create empty vectors to store the simulated values
  V    = matrix(0, nrow = iter, ncol  = n)  # Volatility of log return
  iV   = matrix(0, nrow = iter, ncol  = n)
  Y    = matrix(0, nrow = iter, ncol  = n)  # Log return
  Jv   = matrix(0, nrow = iter, ncol  = n)  # Jumps in volatility
  Jy   = matrix(0, nrow = iter, ncol  = n)  # Jumps in log return
  V[,1] = ETH_result$volatility[length(ETH_result$volatility)]  # Initial value of volatility = previous estimated vol
  iV[,1] = ETH_result$volatility[length(ETH_result$volatility)]
    
  
  for (i in 2:n) {
      if (i>2){
        startIndex = 1+i-2
        endIndex = 1462+i-2
        intermediate_fit <- svcj_model(ethP.df[startIndex:endIndex,])
        iV[,i-1]=intermediate_fit$volatility[length(intermediate_fit$volatility)]
          parameters = intermediate_fit$parameters
            mu = parameters[1,2]
            mu_y = parameters[2,2]  
            sigma_y = parameters[3,2]  
            lambda = parameters[4,2]
            alpha = parameters[5,2]
            beta = parameters[6,2]
            rho = parameters[7,2]
            sigma_v = parameters[8,2]
            rho_j = parameters[9,2]
            mu_v = parameters[10,2]
            kappa = -(alpha/beta)
            theta = alpha/kappa
      }
      Z = mvrnorm(n = iter, mu = c(0,0), Sigma = matrix(c(1,rho,rho,1), nrow = 2))  # Standard normal random value
      Z1 = Z[,1]
      Z2 = Z[,2] 
      J = rbern(n = iter, prob = lambda)  # Bernoulli distributed random value with lambda = 0.051 for determining whether a jump exists
      XV       = rexp(n = iter, rate = 1/mu_v)  # Exponential distributed random value with mV = 0.709 for jump size in volatility
      X        = rnorm(n = iter, mean = mu_y + rho_j * XV, sd = sigma_y)  # Jump size of log return
      #V[i]     = alpha + beta*V[i-1] + sigma_v*sqrt(V[i-1])*Z2 + XV*J  # Volatilty
      V[,i]     = kappa * theta + (1 - kappa) * iV[,i-1] + sigma_v*sqrt(iV[,i-1])*Z2 + XV*J
      Y[,i]     = mu + sqrt(iV[,i-1])*Z1 + X*J  # Log return
      Jv[,i]    = XV*J  # Jumps in volatilty (0 in case of no jump)
      Jy[,i]    = X*J  # Jumps in log return (0 in case of no jump)
      print(paste0("Simulation ",i," of ", n, " for ETH"))
    }



simulated_returnsVol_ETH <- setNames(list(Y, V,iV), 
                                               c("simulated_returns", "simulated_volatility","estimated_volatility"))

save(simulated_returnsVol_ETH, file = "simulated_returns_ETH.Rda")

rm(parameters, alpha, beta, crypto, i, iter, J, 
   Jv, Jy, kappa, lambda, mu, mu_v, mu_y, n, rho, rho_j, sigma_v, sigma_y,
   theta, V, X, XV, Y, Z1, Z2, Z,intermediate_fit,startIndex,endIndex,iV)


#load("simulated_returns_long.Rda")

# # Store a smaller list of simulated returns (to save memory space for the app) 
# simulated_returns_ETH <- list()
#   simulated_returns_ETH <- simulated_returnsVol_ETH$simulated_returns[,1:361]


#save(simulated_returns, file = "simulated_returns.Rda")
#load("simulated_returns.Rda")

# Plot simulated return for ETH
# ggplot() + 
#   geom_line(aes(x = seq(1:1000), y = simulated_returnsVol_ETH$simulated_returns[1,]), col = "black") + 
#   geom_line(aes(x = seq(1:1000), y = simulated_returnsVol_ETH$simulated_returns[1000,]), col = "blue") + 
#   labs(ylab("Daily Returns")) +
#   labs(xlab("Days")) +
#   theme_bw() +
#   theme(panel.grid = element_blank()) 
  
# Plot some simulated price paths for ETH
# init_price <- ETH_initial_train.df$Adj.Close[length(ETH_initial_train.df$Adj.Close)]
# n <- 7
# iter2 <- 5000
# sim_price <- data.frame(matrix(NA, nrow = iter2, ncol = n))
# sim_price[,1] <- init_price
# 
# for (i in 2:n) {
#   sim_price[,i] <- (simulated_returnsVol_ETH$simulated_returns[,i]/sqrt(250) + 1)*sim_price[,i-1] 
# }
# rm(i, init_price, iter2,n)

# Plot some simulated price paths for ETH
# ggplot() + 
#   geom_line(aes(x = seq(1:1000), y = unlist(sim_price[500,])), col = "black") + 
#   geom_line(aes(x = seq(1:1000), y = unlist(sim_price[1000,])), col = "blue") + 
#   geom_line(aes(x = seq(1:1000), y = unlist(sim_price[2501,])), col = "green") +
#   geom_line(aes(x = seq(1:1000), y = unlist(sim_price[3500,])), col = "red") +
#   geom_line(aes(x = seq(1:1000), y = unlist(sim_price[5000,])), col = "purple") +
#   labs(ylab("Daily Returns")) +
#   labs(xlab("Days")) +
#   theme_bw() +
#   theme(panel.grid = element_blank()) 

```

LTC
```{r warning=FALSE}
n      = 21  # Number of observaions in each simulation (i.e number of future days) => row 1 is t0 => 2 = t+1
iter = 5000 # Number of price paths

simulated_returnsVol_LTC = list()


  parameters = LTC_result$parameters
  mu = parameters[1,2]
  mu_y = parameters[2,2]  
  sigma_y = parameters[3,2]  
  lambda = parameters[4,2]
  alpha = parameters[5,2]
  beta = parameters[6,2]
  rho = parameters[7,2]
  sigma_v = parameters[8,2]
  rho_j = parameters[9,2]
  mu_v = parameters[10,2]
  kappa = -(alpha/beta)
  theta = alpha/kappa
  
  # Create empty vectors to store the simulated values
  V    = matrix(0, nrow = iter, ncol  = n)  # Volatility of log return
  iV   = matrix(0, nrow = iter, ncol  = n)
  Y    = matrix(0, nrow = iter, ncol  = n)  # Log return
  Jv   = matrix(0, nrow = iter, ncol  = n)  # Jumps in volatility
  Jy   = matrix(0, nrow = iter, ncol  = n)  # Jumps in log return
  V[,1] = LTC_result$volatility[length(LTC_result$volatility)]  # Initial value of volatility = previous estimated vol
  iV[,1] = LTC_result$volatility[length(LTC_result$volatility)]
    
  
  for (i in 2:n) {
      if (i>2){
        startIndex = 1+i-2
        endIndex = 1462+i-2
        intermediate_fit <- svcj_model(ltcP.df[startIndex:endIndex,])
        iV[,i-1]=intermediate_fit$volatility[length(intermediate_fit$volatility)]
          parameters = intermediate_fit$parameters
            mu = parameters[1,2]
            mu_y = parameters[2,2]  
            sigma_y = parameters[3,2]  
            lambda = parameters[4,2]
            alpha = parameters[5,2]
            beta = parameters[6,2]
            rho = parameters[7,2]
            sigma_v = parameters[8,2]
            rho_j = parameters[9,2]
            mu_v = parameters[10,2]
            kappa = -(alpha/beta)
            theta = alpha/kappa
      }
      Z = mvrnorm(n = iter, mu = c(0,0), Sigma = matrix(c(1,rho,rho,1), nrow = 2))  # Standard normal random value
      Z1 = Z[,1]
      Z2 = Z[,2] 
      J = rbern(n = iter, prob = lambda)  # Bernoulli distributed random value with lambda = 0.051 for determining whether a jump exists
      XV       = rexp(n = iter, rate = 1/mu_v)  # Exponential distributed random value with mV = 0.709 for jump size in volatility
      X        = rnorm(n = iter, mean = mu_y + rho_j * XV, sd = sigma_y)  # Jump size of log return
      #V[i]     = alpha + beta*V[i-1] + sigma_v*sqrt(V[i-1])*Z2 + XV*J  # Volatilty
      V[,i]     = kappa * theta + (1 - kappa) * iV[,i-1] + sigma_v*sqrt(iV[,i-1])*Z2 + XV*J
      Y[,i]     = mu + sqrt(iV[,i-1])*Z1 + X*J  # Log return
      Jv[,i]    = XV*J  # Jumps in volatilty (0 in case of no jump)
      Jy[,i]    = X*J  # Jumps in log return (0 in case of no jump)
      print(paste0("Simulation ",i," of ", n, " for LTC"))
    }



simulated_returnsVol_LTC <- setNames(list(Y, V,iV), 
                                               c("simulated_returns", "simulated_volatility","estimated_volatility"))

save(simulated_returnsVol_LTC, file = "simulated_returns_LTC.Rda")

rm(parameters, alpha, beta, crypto, i, iter, J, 
   Jv, Jy, kappa, lambda, mu, mu_v, mu_y, n, rho, rho_j, sigma_v, sigma_y,
   theta, V, X, XV, Y, Z1, Z2, Z,intermediate_fit,startIndex,endIndex,iV)

```

GARCH
```{r}
library(TSA)
library(forecast)
library(tseries)
library(ggplot2)
library(fGarch)
library(rugarch)

train_startDate = as.Date("2017-11-09")
train_endDate = as.Date("2021-11-09")

test_startDate = as.Date("2021-11-10")
test_endDate = as.Date("2021-11-30")

train_dates <- seq(train_startDate, train_endDate, "days")
test_dates <- seq(test_startDate, test_endDate, "days")
roll_dates <- seq(train_startDate, test_endDate, "days")
```
```{r}
roll_btcP.ts <-ts(data = as.numeric(btcP.df$Adj.Close),frequency = 365, start = c(2017,as.numeric(format(roll_dates[1], "%j"))))
roll_ethP.ts <-ts(data = as.numeric(ethP.df$Adj.Close),frequency = 365, start = c(2017,as.numeric(format(roll_dates[1], "%j"))))
roll_ltcP.ts <-ts(data = as.numeric(ltcP.df$Adj.Close),frequency = 365, start = c(2017,as.numeric(format(roll_dates[1], "%j"))))

btc_logR <-diff(log(roll_btcP.ts))
eth_logR <-diff(log(roll_ethP.ts))
ltc_logR <-diff(log(roll_ltcP.ts))
```
```{r}
BTC_spec <- ugarchspec(variance.model = list(
      model = "iGARCH", garchOrder = c(1, 1)), 
    mean.model = list(
      armaOrder = c(0,0), 
      include.mean = TRUE), 
    distribution.model = "std")
#BTCGARCH <- ugarchfit(BTC_spec,btc_logR,solver = 'hybrid')
BTCfit = ugarchroll(BTC_spec, btc_logR, solver = 'hybrid', n.ahead = 1,forecast.length = 20, refit.every = 1, refit.window = "moving", calculate.VaR = TRUE,VaR.alpha = c(0.1,0.05),keep.coef = TRUE)
report(BTCfit,type="VaR",VaR.alpha = 0.05, conf.level = 0.95)
report(BTCfit,type="VaR",VaR.alpha = 0.10, conf.level = 0.90)
```
```{r}
ETH_spec <- ugarchspec(variance.model = list(
      model = "iGARCH", garchOrder = c(1, 1)), 
    mean.model = list(
      armaOrder = c(2,10), 
      include.mean = TRUE), 
    distribution.model = "std")

ETHfit = ugarchroll(ETH_spec, eth_logR, solver = 'hybrid', n.ahead = 1,forecast.length = 20, refit.every = 1, refit.window = "moving", calculate.VaR = TRUE,VaR.alpha = c(0.1,0.05),keep.coef = TRUE)
report(ETHfit,type="VaR",VaR.alpha = 0.05, conf.level = 0.95)
report(ETHfit,type="VaR",VaR.alpha = 0.10, conf.level = 0.90)
```

```{r}
LTC_spec <- ugarchspec(variance.model = list(
      model = "iGARCH", garchOrder = c(1, 1)), 
    mean.model = list(
      armaOrder = c(0,0), 
      include.mean = TRUE), 
    distribution.model = "std")

LTCfit = ugarchroll(LTC_spec, eth_logR, solver = 'hybrid', n.ahead = 1,forecast.length = 20, refit.every = 1, refit.window = "moving", calculate.VaR = TRUE,VaR.alpha = c(0.1,0.05),keep.coef = TRUE)
report(LTCfit,type="VaR",VaR.alpha = 0.05, conf.level = 0.95)
report(LTCfit,type="VaR",VaR.alpha = 0.10, conf.level = 0.90)
```
**VaR for SVCJ**

```{r}
load("simulated_returns_BTC.Rda")
load("simulated_returns_ETH.Rda")
load("simulated_returns_LTC.Rda")
```
```{r}
actualR_BTC <- c(0,nrow=20)
index = 1462
for (i in 1:20){
  actualR_BTC[i] <- diff(log(btcP.df$Adj.Close))[index]
  index= index+1
}

VaR05_BTC <- c(0, nrow=20)
VaR10_BTC <- c(0, nrow=20)
for (i in 1:20){
  VaR05_BTC[i] <-as.numeric(quantile(simulated_returnsVol_BTC$simulated_returns[,i+1]/sqrt(250),0.05))
  VaR10_BTC[i] <-as.numeric(quantile(simulated_returnsVol_BTC$simulated_returns[,i+1]/sqrt(250),0.10))
}
```
```{r}
library("rugarch")
```
```{r}
BTC_SVCJ_VAR05 <-VaRTest(alpha = 0.05, actual = as.vector(actualR_BTC), VaR = as.vector(VaR05_BTC), conf.level = 0.95)
show(BTC_SVCJ_VAR05$cc.LRp)
```
```{r}
BTC_SVCJ_VAR10 <-VaRTest(alpha = 0.10, actual = as.vector(actualR_BTC), VaR = as.vector(VaR10_BTC), conf.level = 0.95)
show(BTC_SVCJ_VAR10$cc.LRp)
```
ETH
```{r}
actualR_ETH <- c(0,nrow=20)
index = 1462
for (i in 1:20){
  
  actualR_ETH[i] <- diff(log(ethP.df$Adj.Close))[index]
  index= index+1
}

VaR05_ETH <- c(0, nrow=20)
VaR10_ETH <- c(0, nrow=20)
for (i in 1:20){
  VaR05_ETH[i] <-as.numeric(quantile(simulated_returnsVol_ETH$simulated_returns[,i+1]/sqrt(250),0.05))
  VaR10_ETH[i] <-as.numeric(quantile(simulated_returnsVol_ETH$simulated_returns[,i+1]/sqrt(250),0.10))
}
```
```{r}
ETH_SVCJ_VAR05 <-VaRTest(alpha = 0.05, actual = as.numeric(actualR_ETH), VaR = as.numeric(VaR05_ETH), conf.level = 0.95)
show(ETH_SVCJ_VAR05$cc.LRp)
ETH_SVCJ_VAR10 <-VaRTest(alpha = 0.10, actual = as.numeric(actualR_ETH), VaR = as.numeric(VaR10_ETH), conf.level = 0.95)
show(ETH_SVCJ_VAR10$cc.LRp)
```
LTC
```{r}
actualR_LTC <- c(0,nrow=20)
index = 1462
for (i in 1:20){
  
  actualR_LTC[i] <- diff(log(ltcP.df$Adj.Close))[index]
  index= index+1
}

VaR05_LTC <- c(0, nrow=20)
VaR10_LTC <- c(0, nrow=20)
for (i in 1:20){
  VaR05_LTC[i] <-as.numeric(quantile(simulated_returnsVol_LTC$simulated_returns[,i+1]/sqrt(250) ,0.05))
  VaR10_LTC[i] <-as.numeric(quantile(simulated_returnsVol_LTC$simulated_returns[,i+1]/sqrt(250) ,0.10))
}
```
```{r}
LTC_SVCJ_VAR05 <-VaRTest(alpha = 0.05, actual = as.numeric(actualR_LTC), VaR = as.numeric(VaR05_LTC), conf.level = 0.95)
show(LTC_SVCJ_VAR05$cc.LRp)
LTC_SVCJ_VAR10 <-VaRTest(alpha = 0.10, actual = as.numeric(actualR_LTC), VaR = as.numeric(VaR10_LTC), conf.level = 0.95)
show(LTC_SVCJ_VAR10$cc.LRp)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

